An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-23 poly-embed-journal/poly-embed-journal.tex
Fixing typoe

\subsubsection{Constructuon}
To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Such separated link is given by Construction~\ref{const:eps-thick-link} below.

>>>>

\subsubsection{Construction}
To prove Theorem \ref{thm:link-main}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Such separated link is given by Construction~\ref{const:eps-thick-link} below.
